\plaintitle

### 2017-06-17 papers/IoT2017/analysis.tex
no message

This section presents a semi-formal analysis of our proposed solution
and shows that it satisfies the security, safety, and privacy
requirements formulated earlier.

\subsection{Security}
Satisfaction of the security requirements follows from:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item non-malleability of transactions in the distributed ledger,
\item validity conditions of the transactions, which include conditions on both signatures and asset balances,
\item and tamper-resistance of smart meters.
\end{itemize}
Together, these properties ensure that only the right entities may
create and sign a transaction, that transactions adhere to the rules
of the trading process, and that transactions cannot be tampered
with.\footnote{Due to lack of space, we leave a detailed discussion
  and proof for future work.}

\subsection{Safety}
We now demonstrate that faulty or malicious prosumers cannot trade
excessive amounts of energy if normal prosumers follow the rules of
the trading process.
%
First, we can show that the net amount of energy sold by prosumer $i$ for
each timestep is at most $\field{MAXEPA}_i$.  By definition, the
amount of energy sold is less than or equal to the amount of EPA
obtained by prosumer $i$.  A prosumer can obtain EPA either by
withdrawing from its smart meter or by purchasing form another
prosumer.  From its smart meter, prosumer $i$ can withdraw at most
$\field{MAXEPA}_i$.
% amount of EPA.
Although the prosumer may also buy EPA from another prosumer, this
constitutes buying energy, which decreases the net amount of energy
sold with the same amount.
%However, to obtain more EPA, the prosumer has to buy energy from another prosumer, which would decrease its net energy sold by the same amount.
Hence, the net amount of energy sold by prosumer $i$ cannot exceed
$\field{MAXEPA}_i$.  By extending the argument, we can show that the net
amount of energy sold by a group of prosumers~$G$ cannot exceed
$\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, we can show that the net
amount of energy bought by a group of prosumers $G$ cannot exceed
$\sum_{i \in G} \field{MAXECA}_i$.

Using a similar argument, we can also show that the total amount of energy bids (or asks) posted at
the same time by prosumer $i$ for each timestep is at most
$\field{MAXEPA}_i + \field{MAXECA}_i$.  This limit is higher than for
net energy sold or bought, since prosumer $i$ may purchase
$\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA)
from other prosumers, and then post an energy ask (or bid) in the
amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.

\subsection{Privacy}
Due to our use of communication anonymity and mixing services, members
of a microgrid can observe only the amount of assets withdrawn by a
prosumer from its smart meter.
% the amount of energy and financial assets withdrawn by a prosumer.
Since all trading transactions are anonymous, they do not reveal the
actual amount of assets traded by the prosumer.  If a prosumer has not traded away all of its assets, %is left with assets that were not traded, % does not wish to trade, 
then it can also anonymously deposit the remainder to
a random address that was freshly generated by its smart meter. Note that even
if a prosumer does not wish to trade, it should always
withdraw, mix, and deposit the same amount of assets.  Otherwise, the
lack (or varying amount) of withdrawal would leak information.

>>>>

This section presents a semi-formal analysis of PETra
and shows that it satisfies the security, safety, and privacy
requirements formulated earlier.

\subsection{Security}
Satisfaction of the security requirements follows from:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item immutability of transactions in the distributed ledger,
\item validity conditions of the transactions, which include conditions on both signatures and asset balances,
\item and tamper-resistance of smart meters.
\end{itemize}
Together, these properties ensure that only the right entities may
create and sign a transaction, that transactions adhere to the rules
of the trading workflow, and that transactions cannot be tampered
with.\footnote{Due to lack of space, we leave a detailed discussion
  and proof for future work.}

\subsection{Safety}
We now demonstrate that faulty or malicious prosumers cannot trade
excessive amounts of energy if normal prosumers follow the rules of
the trading workflow.
%
First, we can show that the net amount of energy sold by prosumer $i$ for
each timestep is at most $\field{MAXEPA}_i$.  By definition, the
amount of energy sold is less than or equal to the amount of EPA
obtained by prosumer $i$.  A prosumer can obtain EPA either by
withdrawing from its smart meter or by purchasing form another
prosumer.  From its smart meter, prosumer $i$ can withdraw at most
$\field{MAXEPA}_i$.
Although the prosumer may also buy EPA from another prosumer, this
constitutes buying energy, which decreases the net amount of energy
sold with the same amount.
Hence, the net amount of energy sold by prosumer $i$ cannot exceed
$\field{MAXEPA}_i$.  By extending the argument, we can show that the net
amount of energy sold by a group of prosumers~$G$ cannot exceed
$\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, we can show that the net
amount of energy bought by a group of prosumers $G$ cannot exceed
$\sum_{i \in G} \field{MAXECA}_i$.

%Using a similar argument, we can also show that the total amount of energy bids (or asks) posted at
%the same time by prosumer $i$ for each timestep is at most
%$\field{MAXEPA}_i + \field{MAXECA}_i$.  This limit is higher than for
%net energy sold or bought, since prosumer $i$ may purchase
%$\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA)
%from other prosumers, and then post an energy ask (or bid) in the
%amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.

\subsection{Privacy}
Due to our use of communication anonymity and mixing services, members
of a microgrid can observe only the amount of assets withdrawn by a
prosumer from its smart meter.
Since all trading transactions are anonymous, they do not reveal the
actual amount of assets traded by the prosumer.  If a prosumer has not traded away all of its assets, 
then it can also anonymously deposit the remainder to
a random address that was freshly generated by its smart meter. Note that even
if a prosumer does not wish to trade, it should always
withdraw, mix, and deposit the same amount of assets.  Otherwise, the
lack (or varying amount) of withdrawal would leak information.

### 2017-06-17 papers/IoT2017/concl.tex
no message

\Doug{Abhishek, as always, it would be best if we could revise this summary of the paper's contents to be a summary of lessons learned based upon our experiences to date!}
As the complexity of power systems increases due to the evolution of
power grids, decentralized transactive-energy IoT systems are emerging
to tackle this complexity. Ironically, these decentralized systems
also give rise to new privacy challenges. %, such as ...
\Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}
These privacy challenges are exacerbated by the stringent safety and
security requirements of power systems.

This paper describes how we address these challenges via an
innovative solution for anonymous energy trading within a transactive
microgrid.  Our solution builds on distributed ledgers, such as
blockchains, and other proven techniques for anonymity, such as mixing
services and onion routing.  We described our robust process of
anonymous energy trading and explained the novel transactions and
services used in our system.  Finally, we discussed how the proposed
solution satisfies security, safety, and privacy requirements.  In
future work, we will provide rigorous proofs of satisfying these
requirements, and we will present an implementation of our system with
performance results.

>>>>

\Doug{Abhishek, as always, it would be best if we could revise this summary of the paper's contents to be a summary of lessons learned based upon our experiences to date!}
As the complexity of power systems increases due to the evolution of
power grids, decentralized transactive-energy IoT systems are emerging
to tackle this complexity. Ironically, these decentralized systems
also give rise to new privacy challenges,
\Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}
which are exacerbated by the stringent safety and
security requirements of power systems.

This paper describes \change{how we address these challenges via}{\emph{Privacy-preserving Energy Transactions} (PETra),} an
innovative solution for anonymous energy trading within a transactive
microgrid.  PETra builds on distributed ledgers, such as
blockchains, and proven techniques for anonymity, such as mixing
services and onion routing.  We described the workflow of
anonymous energy trading and explained the novel transactions and
services used in PETra.  Finally, we discussed how PETra
 satisfies security, safety, and privacy requirements.  In
future work, we will provide rigorous proofs of satisfying these
requirements, and we will present an implementation of PETra with
performance results.

### 2017-06-17 papers/IoT2017/intro.tex
update
no message

Power grids are undergoing major changes due to rapid
acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. 
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
battery technology costs per kWh have dropped significantly
\cite{stock2015powerful}, reaching grid parity.
%\cite{bronski2015economics}
This massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\emph{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

@@

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising of smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as applications of
IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are
the next step for the smart grid.
% With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible.

In general, the focus is now on creating a distributed IoT
infrastructure
%  comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator
that provides the necessary computation fabric to support the
interplay between energy control and fiscal market challenges, as
shown by Volttron \cite{katipamula2016volttron}, OpenFMB
\cite{gunthersmart}, and the Resilient Information Architecture
Platform for Smart Grid (RIAPS)
\cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a
distributed IoT operating system that provides the foundations for all
algorithms, isolates the hardware details from the algorithms, and
provides essential mechanisms for resource management, fault
tolerance, and security. Most of these efforts, however, focus on the
computation and distribution of information, and do not provide the
support required to handle the privacy challenges that arise from the
required information exchange in this decentralized transactive
system.

This paper assumes the existence of a distributed IoT infrastructure
and specifically focuses on the following privacy challenges:
%
%
% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
%
%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
%\Aron{I'll probably just remove this.}
%Specifically, 
%in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
%electric grids need to become more decentralized.
%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
 Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. In comparison, secure
  smart metering reveals the prosumers' energy usage patterns only to
  the operator.

\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
 \Abhishek{Is this not
  related to the first point?  Perhaps the first point can be just
  about identity and second point can be specifically about
  consumption patterns.}\Aron{The first point is about to whom
  information might be leaked, and the second point is about the type
  of information. I'll make this more clear.}  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\emph{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play an important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
  Transactions and energy
  usage data in a transactive microgrid are much richer sources of
  information than the simple energy usage data collected by smart
  meters.  More specifically, the information available in a
  transactive microgrid is a superset of what is available from smart
  metering, and it may be used to infer personal information, such as
  risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

@@

\Abhishek{Can we cite an example of such a service?}  \Aron{I am not
  sure what you mean by ``such a service.''}  \Abhishek{We should
  connect the paper and our work back to IoT in this paragraph.}  This
paper proposes a solution that (1) enables trading energy futures in a
secure and verifiable manner, (2) preserves prosumer privacy, and (3)
enables DSOs to regulate the trading platform and enforce certain
safety rules.  \Aron{Since SIGCHI does not have section numbers, this
  paragraph, which describes the organization of the paper, is not
  very clear.}  We first describe the basic components of a
transactive IoT microgrid and formulate security, safety, and privacy
requirements.  Next, we introduce a decentralized system for
transactive microgrids based on distributed ledgers and describe the
transactions and services used to implement this system.  We then
discuss how the system satisfies the security, safety, and privacy
requirements.  Finally, we give a brief overview of related work and
offer concluding remarks.

>>>>

Power grids are undergoing major changes due to rapid
acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. 
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
battery technology costs per kWh have dropped significantly
\cite{stock2015powerful}, reaching grid parity.
% \cite{bronski2015economics}
This massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\emph{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

@@

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising of smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as applications of
IoT in smart grid~\cite{Haider2016166}. Transactive grid is the next step \cite{collier2017emerging}.

In general, the focus is now on creating a distributed IoT
infrastructure
that provides the necessary computation fabric to support the
interplay between energy control and fiscal market challenges, as
shown by Volttron \cite{katipamula2016volttron}, OpenFMB
\cite{gunthersmart}, and the Resilient Information Architecture
Platform for Smart Grid (RIAPS)
\cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a
distributed IoT operating system that provides the foundations for all
algorithms, isolates the hardware details from the algorithms, and
provides essential mechanisms for resource management, fault
tolerance, and security. Most of these efforts, however, focus on the
computation and distribution of information, and do not provide the
support required to handle the privacy challenges that arise from the
required information exchange in this decentralized transactive
system.

This paper assumes the existence of a distributed IoT infrastructure
and specifically focuses on the following privacy challenges:
\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
\item \textbf{Leakage of Energy Usage Patterns to Other Prosumers} 
 Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. In comparison, secure
  smart metering reveals the prosumers' energy usage patterns only to
  the operator.

\item \textbf{Inference of Future States of a Prosumer} 
 \Abhishek{Is this not
  related to the first point?  Perhaps the first point can be just
  about identity and second point can be specifically about
  consumption patterns.}\Aron{The first point is about to whom
  information might be leaked, and the second point is about the type
  of information. I'll make this more clear.}  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\emph{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play an important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

\item \textbf{Personally Identifiable Information} 
  Transactions and energy
  usage data in a transactive microgrid are much richer sources of
  information than the simple energy usage data collected by smart
  meters.  More specifically, the information available in a
  transactive microgrid is a superset of what is available from smart
  metering, and it may be used to infer personal information, such as
  risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

@@

In this paper, we \change{describe an overview of the transactive sequence between different components of the systems. We also describe in the detail the structure of these transactions and show how these transactions}{propose \emph{Privacy-preserving Energy Transactions} (PETra), a distributed-ledger based solution that} (1) enables trading energy futures in a
secure and verifiable manner, (2) preserves prosumer privacy, and (3)
enables DSOs to regulate the trading platform and enforce certain
safety rules. 
%
\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}  
We first describe the basic components of a
transactive IoT microgrid and formulate security, safety, and privacy
requirements.  Next, we introduce PETra and describe the
transactions and services used to implement it.  We then
discuss how PETra satisfies the security, safety, and privacy
requirements.  Finally, we give a brief overview of related work and
offer concluding remarks.

### 2017-06-17 papers/IoT2017/paper.tex
no message

@@

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which may arrange
local communities into transactive microgrids.  Within a transactive
microgrid, consumers with energy generation and storage capabilities
can trade energy with each other, thereby smoothing the load on the
main grid using local supply. However, it is hard to provide
security, safety, and privacy in a decentralized and transactive
energy system.  On the one hand, consumers' personal information must
be protected from their trade partners and \Abhishek{To what extent is
  this different that the information already known by the system
  operator? Is this more related to the ``real-time'' nature of
  transactive information?  Rather than aggregative total information
  which is available at the end of billing cycle today.} \Aron{Do we
  need to detail this in the abstract?}\Abhishek{we dont have to} the
system operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes our secure and safe solution for
transactive microgrids, which enables consumers to trade energy
without sacrificing their privacy.  Our solution builds on distributed
ledgers, such as blockchains, and provides anonymity for
communication, bidding, and trading.
\end{abstract}

>>>>

\usepackage[normalem]{ulem}
\newcommand{\change}[2]{\textcolor{red}{\sout{#1}} \textcolor{blue}{#2}}
%\newcommand{\change}[2]{#2} % DO NOT DISPLAY CHANGES

@@

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which may arrange
local communities into transactive microgrids.  Within a transactive
microgrid, consumers with energy generation and storage capabilities
can trade energy with each other, thereby smoothing the load on the
main grid using local supply. However, it is hard to provide
security, safety, and privacy in a decentralized and transactive
energy system.  On the one hand, consumers' personal information must
be protected from their trade partners and \Abhishek{To what extent is
  this different that the information already known by the system
  operator? Is this more related to the ``real-time'' nature of
  transactive information?  Rather than aggregative total information
  which is available at the end of billing cycle today.} \Aron{Do we
  need to detail this in the abstract?}\Abhishek{we dont have to} the
system operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes \change{our}{\emph{Privacy-preserving Energy Transactions} (PETra), a} secure and safe solution for
transactive microgrids, which enables consumers to trade energy
without sacrificing their privacy.  \change{Our solution}{PETra} builds on distributed
ledgers, such as blockchains, and provides anonymity for
communication, bidding, and trading.
\end{abstract}

### 2017-06-17 papers/IoT2017/prelim.tex
no message

\section{Preliminaries and Requirements}
\Aron{Redundant, previous and following paragraphs state what we do here anyway.}
This section describes the basic components of a transactive IoT
microgrid and formulates security, safety, and privacy requirements.

\subsection{Transactive Microgrid Components}

\Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
We begin by describing a basic system model of decentralized 
\Doug{Abhishek, if there's room can we add a diagram showing how all these components relate to each other?} 
transactive IoT microgrids.  We discuss the following components: a
distributed ledger for recording transactions, a bid storage service
that facilitates finding trade partners, a microgrid controller for
regulating the microgrid load, and smart meters for measuring the
prosumers' energy production and consumption.

@@

\subsubsection{Bid Storage Service}
Although prosumers trade energy with each other directly (\emph{i.e.},
without a middleman), for the sake of scalability, we need a service
that enables prosumers to find trade partners.
%A bid storage service receives energy buy and sell bids from prosumers, stores these 
We assume that there is a bid storage service that allows prosumers to
post and read energy \emph{bids} and \emph{asks}.\footnote{A
  \emph{bid} is an offer to buy at a certain price, while an
  \emph{ask} is an offer to sell at a certain price.}  This service
relieves prosumers from contacting a large number of potential trade
partners since they only communicate with the service to discover
trade partners.
%Moreover, in addition to simply storing bids and asks, the service may also find matches in the posted bids and asks, and it may notify the posting prosumers of the trade opportunity.
To enhance scalability and reliability, this service can also be
implemented in a distributed manner, using multiple nodes.

\subsubsection{Microgrid Controller}
\Aron{Is this true?}
The microgrid controller stabilizes the load within the microgrid
based on the predicted future load within the microgrid and the rest
of the grid.  The controller first predicts load in the microgrid
based on (1) bids and asks in the bid storage and (2) outstanding
energy trades in the ledger.  By combining this information with the
prediction for the rest of the grid, the controller produces a control
signal that specifies how much the microgrid load should be decreased
or increased.  Based on this signal, the controller then updates the
price policy for the microgrid to influence energy production and
consumption.  We also assume the presence of a secondary controller
that balances voltage and frequency in the microgrid.

@@

\subsubsection{Security}
Security requirements ensure primarily that prosumers are billed
correctly, but they also provide necessary prerequisite properties for
safety.
%Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
More specifically, they require that
\begin{itemize}[noitemsep,topsep=-\parskip]
\item prosumers are billed correctly based on the energy prices set by
  the DSO, their energy trades, and their actual energy production and
  consumption measured by the smart meters,
% (i.e., prosumers or outside attackers cannot tamper with energy production, consumption, and financial balances) % attackers cannot tamper with energy production and consumption balances or financial balances),
\item prosumers or outside attackers cannot change microgrid
  regulatory policies that are set by the DSO, 
\item prosumers cannot back out of trades unilaterally, and they
  cannot tamper with other prosumers' trading or bidding,
\item financial and physical impact of compromised or faulty nodes is
  limited, and nodes can be banned by the DSO. 
\end{itemize}

\subsubsection{Safety}
A careless or malicious prosumer may destabilize the grid by promising
to produce (or consume) a large amount of energy, but failing to actually
produce (or consume) it.  A significant difference between promised and
actual energy production (or consumption) can result in a large gap
between the aggregate production and consumption of the microgrid.
A large gap threatens the stability of not only the microgrid but also the main
power grid.  Therefore, prosumers should not be able to trade large
amounts of energy that they are unlikely to deliver.
%Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
Specifically, we require that 
\begin{itemize}[noitemsep,topsep=-\parskip]
\item the net amount of energy sold (or bought) by a prosumer is upper
  bounded (by an amount set by the DSO), where the net amount of
  energy sold is the difference between the amount of energy sold and
  bought by the prosumer, and the net amount of energy bought is
  defined analogously,
\item the energy bids and asks posted by a prosumer are limited in a
  similar way.
\end{itemize}

>>>>

%!TEX root = paper.tex
\section{System Model and Requirements}
\Aron{Redundant, previous and following paragraphs state what we do here anyway.}
This section describes a basic system model of transactive IoT
microgrids and formulates security, safety, and privacy requirements.

\subsection{Transactive Microgrid System Model}
\Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
We begin by describing a basic system model of decentralized 
\Doug{Abhishek, if there's room can we add a diagram showing how all these components relate to each other?} 
transactive IoT microgrids.  We discuss the following components: a
distributed ledger for recording transactions, a bid storage service
that facilitates finding trade partners, a microgrid controller for
regulating the microgrid load, and smart meters for measuring the
prosumers' energy production and consumption.
Figure~\ref{fig:softwareArchitecture} shows the high-level architecture of 
\change{our solution.  In this figure, components marked red are introduced to
provide privacy in a safe and secure manner, whereas components marked
in blue are typical elements of a decentralized transactive microgrid.}{a decentralized transactive microgrid with PETra. 
Components marked in blue are basic elements of the decentralized transactive microgrid,
while components marked in red are added (or extended) by PETra.}

\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=0.9cm, font=\small,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};

\draw [nodeStyle, fill=blue!10] (0, 2.4) rectangle    (1, 3.0) node [midway, align=center] {Distributed ledger (e.g., blockchain)};

\draw [nodeStyle, fill=red!10]  (0, 3.15) rectangle (0.45, 4.05) node [midway, align=center] {Transaction anonymity\\[-0.2em](mixing service)};
\draw [nodeStyle, left color=blue!10, right color=red!10] (0.47, 3.15) rectangle (0.72, 4.05) node [midway, align=center] {Bid storage};
\draw [nodeStyle, left color=blue!10, right color=red!10] (0.74, 3.15) rectangle (1, 4.05) node [midway, align=center] {Active\\[-0.2em]smart meter};

\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]workflow for prosumers};
\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
\end{tikzpicture}
\caption{High-level architecture of a decentralized transactive microgrid with PETra.}
\label{fig:softwareArchitecture}
\end{figure}

@@

\subsubsection{Bid Storage Service}
Although prosumers trade energy with each other directly (\emph{i.e.},
without a middleman), for the sake of scalability, we need a service
that enables prosumers to find trade partners.
We assume that there is a bid storage service that allows prosumers to
post and read energy \emph{bids} and \emph{asks}.\footnote{A
  \emph{bid} is an offer to buy at a certain price, while an
  \emph{ask} is an offer to sell at a certain price.}  This service
relieves prosumers from contacting a large number of potential trade
partners since they only communicate with the service to discover
trade partners.
To enhance scalability and reliability, this service can also be
implemented in a distributed manner, using multiple nodes.

\subsubsection{Microgrid Controller (Distribution System Operator)}
We assume the existence of a controller at the Distribution System Operator level that regulates the total load that the microgrid should present to the distribution system.
 The controller first predicts load in the microgrid
based on (1) bids and asks in the bid storage and (2) outstanding
energy trades in the ledger.  By combining this information with the
prediction for the rest of the grid, the controller produces a control
signal that specifies how much the microgrid load should be decreased
or increased.  Based on this signal, the controller then updates the
price policy for the microgrid to influence energy production and
consumption.  We also assume the presence of a secondary controller
that balances voltage and frequency in the microgrid.

@@

\subsubsection{Security}
Security requirements ensure primarily that prosumers are billed
correctly, but they also provide necessary prerequisite properties for
safety.
More specifically, they require that
\begin{itemize}[noitemsep,topsep=-\parskip]
\item prosumers are billed correctly based on the energy prices set by
  the DSO, their energy trades, and their actual energy production and
  consumption measured by the smart meters,
\item prosumers or outside attackers cannot change microgrid
  regulatory policies that are set by the DSO, 
\item prosumers cannot back out of trades unilaterally, and they
  cannot tamper with other prosumers' trading or bidding,
\item financial and physical impact of compromised or faulty nodes is
  limited, and nodes can be banned by the DSO. 
\end{itemize}

\subsubsection{Safety}
A careless or malicious prosumer may destabilize the grid by promising
to produce (or consume) a large amount of energy, but failing to actually
produce (or consume) it.  A significant difference between promised and
actual energy production (or consumption) can result in a large gap
between the aggregate production and consumption of the microgrid.
A large gap threatens the stability of not only the microgrid but also the main
power grid.  Therefore, prosumers should not be able to trade large
amounts of energy that they are unlikely to deliver.
Specifically, we require that 
\begin{itemize}[noitemsep,topsep=-\parskip]
\item the net amount of energy sold (or bought) by a prosumer is upper
  bounded (by an amount set by the DSO), where the net amount of
  energy sold is the difference between the amount of energy sold and
  bought by the prosumer, and the net amount of energy bought is
  defined analogously. %,
%\item the energy bids and asks posted by a prosumer are limited in a similar way.
\end{itemize}

### 2017-06-17 papers/IoT2017/related.tex
no message

Our solution extends this earlier work by considering a decentralized
IoT system for transactive energy, and addressing the novel privacy
threat posed by trading. In particular, while earlier results
protected the prosumers' privacy from the DSO, we protect privacy from
other prosumers as well as from outside attackers.

>>>>

PETra extends this earlier work by considering a decentralized
IoT system for transactive energy, and addressing the novel privacy
threat posed by trading. In particular, while earlier results
protected the prosumers' privacy from the DSO, we protect privacy from
other prosumers as well as from outside attackers.
